Life in the canopy: Phylogenetic filtering and morphological canalization in epiphytic ferns

### 2019-06-24 ms/manuscript.Rmd
Add figures

---
title: "Life in the canopy: Phylogenetic filtering and morphological canalization in epiphytic ferns"
bibliography: "references_clean.bib"
output: word_document
csl: "new-phytologist.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

>>>>

---
title: "Life in the canopy: Phylogenetic filtering and morphological canalization in epiphytic ferns"
bibliography: "references.bib"
mainfont: Roboto-Regular.ttf
fontsize: 12pt
mainfontoptions: 
- BoldFont=Roboto-Bold.ttf
- ItalicFont=Roboto-Italic.ttf
- BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
  bookdown::word_document2:
    toc: no
    fig_caption: yes
    pandoc_args: [ "--csl", "new-phytologist.csl"]
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)
library(tidyverse)
library(drake)
library(patchwork)
```

@@

## Materials and Methods

## Results

## Discussion

## Acknowledgements

## Figures

```{r climate-plot, fig.height = 4, fig.width = 6, fig.caption = "climate"}
loadd(climate_plot)
climate_plot
```

```{r pca-plot, fig.height = 6, fig.width = 6, fig.caption = "trait PCA"}
loadd(pca_plot)
pca_plot
```

```{r tree, fig.height = 8, fig.width = 6, fig.caption = "traits on tree"}
loadd(traits_with_tree)
traits_with_tree
```

```{r combined-comm-div-plots, fig.height = 8, fig.width = 6, fig.caption = "community diversity metrics"}
loadd(combined_comm_div_plots)
combined_comm_div_plots
```

```{r combined-cwm-div-plots, fig.height = 8, fig.width = 6, fig.caption = "community-weighted means"}
loadd(combined_cwm_plots)
combined_cwm_plots
```

## Tables

## References
